\chapter{Design specifications}
\section{Front-End-Design}
\begin{itemize}
\item User-Friendly Interface: Easy-to-use design for smooth interaction.
\item Clean and Modern Design: Attractive and up-to-date visuals.
\item Interactive Elements: Effortless actions and data input.
\item Focus on Usability: Simplifying shop management for convenience.
\end{itemize}

\section{Back-End-Design}
Our \textbf{Shop Management System} is built on the Express framework, a fast and minimalist web framework for Node.js. It leverages various packages and models to manage different aspects of the shop, including products, staff, customers, and delivery.

The dependencies used in our backend design include:
\begin{itemize}
    \item \textbf{express}: Fast, unopinionated, and minimalist web framework for Node.js.
    \item \textbf{productmodel}: Model for managing product data.
    \item \textbf{staffmodel}: Model for managing staff data.
    \item \textbf{customermodel}: Model for managing customer data.
    \item \textbf{deliverymodel}: Model for managing delivery man data.
\end{itemize}
Our Express app serves as the main entry point for the backend, handling routes, middleware, and server configuration. We utilize the following middleware:
\begin{itemize}
    \item \textbf{cors}: Middleware for enabling Cross-Origin Resource Sharing.
    \item \textbf{bodyParser}: Middleware for parsing HTTP request bodies.
\end{itemize}

The backend runs on port \texttt{3001}, and the server listens for incoming requests on this port.


\section{Implementation Requirements}
The successful implementation of the \textbf{Shop Management System} requires the following:

\subsection{Hardware Requirements}
\begin{itemize}
    \item A computer with a minimum of 4GB RAM.
    \item Sufficient storage capacity to accommodate the software and database.
    \item A stable internet connection for accessing the system.
\end{itemize}

\subsection{Software Requirements}
\begin{itemize}
    \item Web Browser: Google Chrome, Mozilla Firefox, or Microsoft Edge.
    \item Node.js: Version 12 or above.
    \item Express.js: Version 4 or above.
\end{itemize}

\subsection{Development Tools}
\begin{itemize}
    \item Integrated Development Environment (IDE): Visual Studio Code.
    \item Package Manager: npm (Node Package Manager).
\end{itemize}

\subsection{Third-Party Libraries and Frameworks}
\begin{itemize}
    \item Express.js: Fast and minimalist web framework for Node.js.
    \item body-parser: Middleware for parsing HTTP request bodies.
    \item cors: Middleware for enabling Cross-Origin Resource Sharing.
\end{itemize}

It is essential to fulfill these requirements to guarantee the smooth implementation and functionality of the \textbf{Shop Management System}.

\section{Summary}
The implementation requirements for the \textbf{Shop Management System} encompass several key components. A stable internet connection is essential for seamless communication between the software and the users. 