\section{Software Requirements}
To develop a Shop Management System, the following software requirements are used:

\begin{enumerate}
\item \textbf{React}: A JavaScript library for creating interactive user interfaces in web development.
\item \textbf{Node.js}: A runtime environment used for server-side development, allowing the system to handle server logic and connect with databases and APIs.
\item \textbf{XAMPP}: A software package that includes an Apache web server, MySQL database, and PHP, providing a local testing environment for the system.
\item \textbf{Bootstrap}: A popular framework with pre-designed components and stylesheets, making it easier to create visually appealing and mobile-friendly interfaces.
\item \textbf{Chart.js}: A JavaScript library for visualizing data, enabling the creation of various charts and graphs to display sales data and analytics within the system.
\end{enumerate}
These software requirements form the essential components for developing a robust and functional Shop Management Software System. They cover frontend and backend technologies, database management, and data visualization capabilities.\\
\begin{enumerate}
\item \textbf{Express.js}: A web application framework for Node.js, Express.js is used to build the backend API and handle HTTP requests and responses.
\item \textbf{JWT (JSON Web Tokens)}: JWT is employed for authentication and secure communication between the client and server, ensuring that only authorized users can access the system.

\item \textbf{Email Notifications}: The system can be equipped with email notification functionality to send automated order confirmations, shipping updates, and promotional offers to customers.
\end{enumerate}

These additional requirements enhance the functionality and user experience of the Shop Management System, ensuring secure authentication, seamless payment processing, efficient communication, and enhanced customer engagement.\\
\section{Design Requirements:}
\begin{itemize}
\item User-friendly interface for efficient navigation and task performance.
\item Responsive design to ensure consistent user experience across devices.
\item Robust database design for efficient storage and retrieval of shop-related data.
\item Scalability to accommodate increasing data volumes and user traffic.
\item Strong security measures to protect sensitive shop data.
\item Reporting and analytics capabilities for generating sales reports and inventory analysis.
\item Integration capabilities with payment gateways, shipping providers, and third-party applications.
\item Customizability options to meet individual shop requirements.
\end{itemize}
\input{SystemAnalysis/use case modelling and description}