\chapter{Limitation , Future scope \& Conclusion}
\section{Limitation}
\vspace{0.2cm}
\begin{itemize}
\item Lack of a dedicated mobile app.
\item Inadequate responsiveness for mobile device and notepad.
\item Dependence on plain CSS for designing user interface.
\item Absence of integration with payment gateways.
\item Lacking of Advanced Filtering options like limited user interface and feature options. 
\item Potential database organization issues like data redundancy , data inconsistency and Lack of Normalization.
\item Inadequate feature of delivery management system.
\end{itemize}

By addressing these limitations and taking proactive measures to mitigate them, businesses can ensure a smoother implementation and optimize the benefits of their shop management software system.
\\[1ex]

\section{Future Scope}
\vspace{0.2cm}

The future scope of our project holds several potential opportunities for expansion and enhancement. Here are some key areas of future development:

\begin{itemize}
\item Global hosting for worldwide accessibility.
\item Integration of globally accepted payment gateways.
\item Enhancing the design for improved feasibility, attractiveness, and responsiveness.
\item Developing a mobile application with additional useful features.
\item Added new features on Delivery Management.
\end{itemize}

By pursuing these future developments, our project can continue to evolve, meet the changing needs of the market, and stay competitive in the dynamic landscape of shop management software systems.\\[1ex]

\section{Conclusion}


Despite the limitations mentioned earlier, our \textbf{Shop Management System} effectively addresses the challenges and requirements of efficient shop management. With its real-time sales management, inventory tools, customer handling, auto-generated payment system, and delivery management system, our software optimizes shop operations, enhances customer satisfaction, and drives business growth. We are confident that the successful implementation of this project will contribute to the long-term success and profitability of our shop, making it a valuable asset in the retail industry.

\vspace{8cm}
\section{References}
\begin{enumerate}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}
    \item\texttt{https://www.wrike.com/project-management-guide/}
    \item\texttt{https://www.edvantis.com/blog/software-development-methodologies/}
    \item\texttt{https://www.geeksforgeeks.org/iterative-incremental-model-in-designing-system/}
    \item\texttt{https://www.aarong.com/}
    \item\texttt{https://www.daraz.com.bd/}   
    \item\texttt{https://www.ryanscomputers.com/}
    \item \texttt{https://www.smarteshopbd.com/}
\end{enumerate}